Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-11-05 paper/main.tex
restructuring of discussion of individual (AO) results

\todo[inline]{how to discuss Bland-Altman-Plots? Please, let's talk about that
shortly}

\todo[inline]{discussion of individual differences? what do the results
suggest???}

@@

% intro
We checked the results of the primary contrast also on the level of individual
subjects to ``test'' the audio-description's performance as a functional
localizer compared to the dedicated visual localizer paradigm.\todo{hm, sounds
meh}
% results of dedicated localizer
The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
12 of 14 subjects and unilateral right ROI in two subjects (sub-04, sub-20).
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI)  and
an unilateral significant cluster in one subject.
% difference
Notably, we here used a ``one fits all approach`` whereas
\citep{sengupta2016extension} chose the best fitting $z$-threshold in a
subject's unthresholded $z$-maps by visual judgment and used the best of three
alternative contrasts (strict, relaxed, or simple contrast).

@@

% conclusion
Our results suggest that a naturalistic auditory stimulus is suitable to
localize (the anterior part) of a higher-level visual area in the majority of
subjects.
% individual contrasts
Nevertheless, studies that primary aim for individual results should
choose individual thresholds and test more than just one contrast to gain the
best (?) individual ROIs.\todo{``best'' always sounds kind of judgmental}
% individual results
Notably, we chose one contrast to look into individual results of all subjects
but individually a contrast different from the primary contrast might lead to
better individual localization results.

\todo[inline]{which contrast works better in which subjects?; if focus is
individual diagnostics take the individually best contrasts; cf. Sengupta}

\todo[inline]{different ``capability'' to process auditory spatial information}

@@

\todo[inline]{was not aim of the study in the first place but conceptual
control}

On individual level, mixed results for AV stimulus.

@@

>>>>

@@

\todo[inline]{``problem'': if discussion of anterior vs. posterior PPA above
turns out that anterior PPA is a submodul of the PPA we do not localize a
``visual area'' with an auditory stimulus}

\todo[inline]{how to discuss Bland-Altman-Plots? Let's talk about that
shortly please}

todo[inline]{in 11 subjects there are voxels of higher z-score (in the PPA ROI)
    in the AO contrast than in the contrast of the visual localizer -> should
    all be in the anterior part of the PPA ROI, i.e. the area that belongs to
    the significant cluster of the AO contrast}

% intro
In order to test the audio-description's performance as a functional localizers,
we also compared the results of the audio-description's primary contrast to
results of the dedicated visualizer on the level of individual subjects.
% results of dedicated localizer
The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
12 of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI)  and
a unilateral significant cluster in one subject.
% conclusion
Results of our exploratory analyses suggest that a naturalistic auditory
stimulus is suitable to localize (the anterior part) of a higher-level visual
area in the majority of subjects.

% one threshold for all
Here we used a ``one threshold fits all approach`` whereas
\citep{sengupta2016extension} chose the best fitting $z$-threshold in a
subject's unthresholded $z$-maps by visual judgment and the ``best fitting''
threshold.
% one contrast for all
Moreover, we chose the same contrast to look at individual results of all
subjects.
% chose the best contrast in the future
Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
alternative contrasts (strict, relaxed, or simple contrast), future studies that
aim for individual diagnostics / ROI localization should also test more than one
contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
shitty}

@@

\todo[inline]{discussion of individual differences? what do the results
suggest? Differences in alterness, attention to spatial information,
predisposition? ``capability'' to process auditory spatial information?}

@@

\todo[inline]{was not aim of the study; AV ROIs are in the plot of individual
    slices but not in the Bland-Altman-Plots}

@@

% future studies: stimulus material
Future studies should probably use a different narrative that models the feature
space of spatial information ``better'' (provides more events that are more
easily classified to belong to distinctive categories).
